Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-03-21 manuscript_rmarkdown/manuscript.Rmd
Correct use of alpha.

Considering single process parameters, the choice of learner (Friedman test: $p < 10^{-8})$), normalisation method (Wilcoxon signed rank test: $p < 10^{-8}$), and transformation method $p = 0.007$, all had a significant impact (at significance level $p = 0.05$).

To estimate the marginal effects of process parameters, including transformation method, we first fit a regression random forest (ranger package [@Wright2017-rf] version 0.16.0): 2000 trees, minimum node size 2, other hyperparameters default) with process parameters and task difficulty as predictors and normalised rank as response variable.
The estimated marginal effects are shown in Figure \ref{fig:marginal-effect-plot}.
On the scale of normalised ranks ($[0.0, 1.0]$), the overall estimated marginal effect of using a random forest instead of generalised linear model was $0.272$.
The overall marginal effect of using z-standardisation to normalise features was $0.008$.
Transformation methods had the following marginal effects:
$0.003$ for using conventional Yeo-Johnson transformation instead of no transformation;
$-0.007$ for using robust invariant Yeo-Johnson transformation instead of no transformation; 
$-0.009$ for using robust invariant Yeo-Johnson transformation with empirical central normality test instead of no transformation; 
$-0.010$ for using robust invariant Yeo-Johnson transformation instead of conventional Yeo-Johnson transformation;
and $-0.012$ for using using robust invariant Yeo-Johnson transformation with empirical central normality test instead of conventional Yeo-Johnson transformation.

>>>>

Considering single process parameters, 
the choice of learner (Friedman test: $p < 10^{-8})$),
normalisation method (Wilcoxon signed rank test: $p = 4 \cdot 10^{-8}$), 
and transformation method (Friedman test:$p = 0.007$,
all had a significant impact (at $p = 0.05$).

To estimate the marginal effects of process parameters, including transformation method, 
we first fit a regression random forest (ranger package [@Wright2017-rf] version 0.16.0): 2000 trees, 
node size 2, other hyperparameters default) with process parameters and task difficulty as predictors and normalised rank as response variable.
The estimated marginal effects are shown in Figure \ref{fig:marginal-effect-plot}.
On the scale of normalised ranks ($[0.0, 1.0]$), the overall estimated marginal effect of using a random forest instead of generalised linear model was $0.272$.
The overall marginal effect of using z-standardisation to normalise features was $0.008$.
Transformation methods had the following marginal effects:
$0.003$ for using conventional Yeo-Johnson transformation instead of no transformation;
$-0.007$ for using robust invariant Yeo-Johnson transformation instead of no transformation; 
$-0.009$ for using robust invariant Yeo-Johnson transformation with empirical central normality test instead of no transformation; 
$-0.010$ for using robust invariant Yeo-Johnson transformation instead of conventional Yeo-Johnson transformation;
and $-0.012$ for using using robust invariant Yeo-Johnson transformation with empirical central normality test instead of conventional Yeo-Johnson transformation.
